### 2023-03-13 main/chapter_2ljets.tex
write generators caption; improve format

Throughout $\twoljets$-electroweak, simulated Monte Carlo samples are the
primary estimates of background and signal processes.
We first simulate samples at `truth-level' by random sampling from
distributions that are implemented by various software packages to approximate
theoretical predictions from quantum field theory.
Simulating events from high-order perturbative quantum field theory is
difficult and computationally expensive, so these implementations use
lower-order approximations, which we normalize to cross-section predictions
that are evaluated at higher precision.
Parton shower programs are used to model the soft QCD evolution of
strongly-interacting particles from the hard scatter down to the low energy
scales of hadronization; because of colour confinement, only these
(colour-neutral) hadrons can survive to interact with the detector.
The various Monte Carlo simulation programs used in this search are summarized
in Table~\ref{tab:2ljets_paper_mc}, which is adapted from the $\twoljets$
paper.
Truth-level results are finally passed through a full simulation of the
\atlas\ detector to simulate `reconstruction-level'
data~\cite{SOFT-2010-01, geant2003}.

@@

\begin{sidewaystable}[tp]
\begin{center}
\scriptsize
\begin{tabular}{llllll}
Physical process &  Generator  & Parton & Cross-section & Tune & PDF set\\
                &             & shower & order in pQCD &      &
\\[0.2em]
\hline
\\[0.2em]
$\ttbar$~\cite{ATL-PHYS-PUB-2016-004}
    & \powhegbox\,v2~\cite{Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
    & \pythia\,8.230~\cite{Sjostrand:2014zea}
    & NNLO+NNLL~\cite{ttbarxsec1,ttbarxsec2,ttbarxsec3,ttbarxsec4,ttbarxsec5}
    & A14~\cite{ATL-PHYS-PUB-2014-021}
    & \textsc{NNPDF2.3lo}~\cite{Ball:2012cx}
\\
$Wt$~\cite{ATL-PHYS-PUB-2016-004}
    & \powhegbox\,v2
    & \pythia\,8.230
    & NNLO+NNLL~\cite{Kidonakis:2010b,Kidonakis:2010tc,Kidonakis:2011wy,Frederix:2012dh}
    & A14
    & \textsc{NNPDF3.0nlo}~\cite{Ball:2014uwa}
\\
$VV$~\cite{ATL-PHYS-PUB-2016-002}
    & \sherpa\,2.2.2~\cite{Bothmann:2019yzt}
    & \sherpa\,2.2.2 & NLO~\cite{diboson1,diboson2}
    & \textsc{Sherpa}~default
    & \textsc{NNPDF3.0nnlo}
\\
$Z/\gamma^{*}(\rightarrow \ell \ell)$\,+\,jets~\cite{ATL-PHYS-PUB-2016-003}
    & \sherpa\,2.2.1
    & \sherpa\,2.2.1
    & NNLO~\cite{DYNNLO1,DYcrosssection}
    & \textsc{Sherpa}~default
    &\textsc{NNPDF3.0nnlo}
\\
Higgs ($\ttbar h$)
    & \powhegbox\,v2
    & \pythia\,8.230
    & NLO~\cite{deFlorian:2016spz}
    & A14
    & \textsc{NPDF2.3lo}
\\
Higgs (VBF, $Vh$)
    & \powhegbox\,v2
    & \pythia\,8.212
    & NNLO~\cite{deFlorian:2016spz}
    & AZNLO~\cite{STDM-2012-23}
    & \textsc{CTEQ6L1}~\cite{Pumplin:2002vw}
\\
Higgs (ggF)
    & \powhegbox\,v2
    & \pythia\,8.212
    & NNNLO~\cite{deFlorian:2016spz}
    & AZNLO
    & \textsc{CTEQ6L1}
\\
$ttt$, $tttt$, $\ttbar$\,+\,$WW$
    & \amcatnlo~\cite{Alwall:2014hca}
    & \pythia\,8.186~\cite{Skands:2014pea}
    & NLO~\cite{Frederix:2017wme,Alwall:2014hca}
    & A14
    & \textsc{NNPDF2.3lo}
\\
$\ttbar$\,+\,$V$~\cite{ATL-PHYS-PUB-2016-005,Garzelli:2012bn}
    & \amcatnlo
    & \pythia\,8.210
    & NLO~\cite{Campbell:2012,Lazopoulos:2008,Alwall:2014hca}
    & \textsc{A14}
    & \textsc{NNPDF2.3lo}
\\
$VVV$~\cite{ATL-PHYS-PUB-2016-002}
    & \sherpa\,2.2.2
    & \sherpa\,2.2.2
    &  NLO~\cite{Bothmann:2019yzt}
    & \textsc{Sherpa}~default
    & \textsc{NNPDF3.0nnlo}
\\
\end{tabular}
\caption{%
Caption TODO
% TODO import citations
% TODO rewrite
% TODO define VBF
% Simulated background event samples used in this analysis with the corresponding matrix element and parton shower generators,
% cross-section order in perturbative QCD used to normalize the event yield, underlying-event tune and PDF set.
% $V$ represents either a $W$ or $Z$ boson.%
Adapted from~\cite{atlas2022searches}.
}
\label{tab:2ljets_paper_mc}
\end{center}
\end{sidewaystable}

>>>>

Throughout $\twoljets$-electroweak, simulated Monte Carlo samples are the
primary estimates of background and signal processes.
We first simulate samples at `truth-level' by random sampling from
distributions with parton distribution functions and scattering matrix elements
that are implemented by various software packages to approximate theoretical
predictions from quantum field theory.
Simulating events from high-order perturbative quantum field theory is
difficult and computationally expensive, so these implementations use
lower-order approximations, which we normalize to cross-section predictions
that are evaluated at higher precision.
Parton shower programs are used to model the soft QCD evolution of
strongly-interacting particles from the hard scatter down to the low energy
scales of hadronization; because of colour confinement, only these
(colour-neutral) hadrons can survive to interact with the detector.
The various Monte Carlo simulation programs used in this search are summarized
in Table~\ref{tab:2ljets_paper_mc}, which is adapted from the $\twoljets$
paper.
Truth-level results are finally passed through a full simulation of the
\atlas\ detector to simulate `reconstruction-level'
data~\cite{SOFT-2010-01, geant2003}.

@@

\begin{sidewaystable}[tp]
\begin{center}
\scriptsize
\begin{tabular}{llllll}
Physical process
    & Generator
    & Parton Shower
    & Cross-section order in QCD
    & Tune
    & PDF set
\\[0.2em]
\hline
\\[0.2em]
$\ttbar$~\cite{ATL-PHYS-PUB-2016-004}
    & \powhegbox\,v2~\cite{Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
    & \pythia\,8.230~\cite{Sjostrand:2014zea}
    & NNLO+NNLL~\cite{ttbarxsec1,ttbarxsec2,ttbarxsec3,ttbarxsec4,ttbarxsec5}
    & A14~\cite{ATL-PHYS-PUB-2014-021}
    & \textsc{NNPDF2.3lo}~\cite{Ball:2012cx}
\\
$Wt$~\cite{ATL-PHYS-PUB-2016-004}
    & \powhegbox\,v2
    & \pythia\,8.230
    & NNLO+NNLL~\cite{Kidonakis:2010b,Kidonakis:2010tc,Kidonakis:2011wy,Frederix:2012dh}
    & A14
    & \textsc{NNPDF3.0nlo}~\cite{Ball:2014uwa}
\\
$VV$~\cite{ATL-PHYS-PUB-2016-002}
    & \sherpa\,2.2.2~\cite{Bothmann:2019yzt}
    & \sherpa\,2.2.2 & NLO~\cite{diboson1,diboson2}
    & \textsc{Sherpa}~default
    & \textsc{NNPDF3.0nnlo}
\\
$Z/\gamma^{*}(\rightarrow \ell \ell)$\,+\,jets~\cite{ATL-PHYS-PUB-2016-003}
    & \sherpa\,2.2.1
    & \sherpa\,2.2.1
    & NNLO~\cite{DYNNLO1,DYcrosssection}
    & \textsc{Sherpa}~default
    &\textsc{NNPDF3.0nnlo}
\\
Higgs ($\ttbar h$)
    & \powhegbox\,v2
    & \pythia\,8.230
    & NLO~\cite{deFlorian:2016spz}
    & A14
    & \textsc{NPDF2.3lo}
\\
Higgs (VBF, $Vh$)
    & \powhegbox\,v2
    & \pythia\,8.212
    & NNLO~\cite{deFlorian:2016spz}
    & AZNLO~\cite{STDM-2012-23}
    & \textsc{CTEQ6L1}~\cite{Pumplin:2002vw}
\\
Higgs (ggF)
    & \powhegbox\,v2
    & \pythia\,8.212
    & NNNLO~\cite{deFlorian:2016spz}
    & AZNLO
    & \textsc{CTEQ6L1}
\\
$ttt$, $tttt$, $\ttbar WW$
    & \amcatnlo~\cite{Alwall:2014hca}
    & \pythia\,8.186~\cite{Skands:2014pea}
    & NLO~\cite{Frederix:2017wme,Alwall:2014hca}
    & A14
    & \textsc{NNPDF2.3lo}
\\
$\ttbar V$~\cite{ATL-PHYS-PUB-2016-005,Garzelli:2012bn}
    & \amcatnlo
    & \pythia\,8.210
    & NLO~\cite{Campbell:2012,Lazopoulos:2008,Alwall:2014hca}
    & \textsc{A14}
    & \textsc{NNPDF2.3lo}
\\
$VVV$~\cite{ATL-PHYS-PUB-2016-002}
    & \sherpa\,2.2.2
    & \sherpa\,2.2.2
    &  NLO~\cite{Bothmann:2019yzt}
    & \textsc{Sherpa}~default
    & \textsc{NNPDF3.0nnlo}
\\
\end{tabular}
\caption{%
Summary of the simulation tools and configurations used for central background
samples in $\twoljets$.
Each row specifies a combination of matrix element generator, parton shower,
and Parton Distribution Function (PDF) components, whose combination we use to
simulate the named physical process.
The tune specifies many parameters of the simulation tools to achieve a good
description of some historical calibration data.
Total sample cross-sections are normalized to a reference value evaluated
at the specified order in perturbative QCD (pQCD).
Symbols:
$V$ is $W$ or $Z$,
VBF is Vector Boson Fusion,
ggF is gluon-gluon Fusion.
This table is adapted from~\cite{atlas2022searches}.
}
\label{tab:2ljets_paper_mc}
\end{center}
\end{sidewaystable}
